### 2016-07-26 notions.tex
comments about privacy

\item An ``indistinguishability'' definition where either $S_0$ or $S_1$ is used, and the attacker
must determine which. Here the attacker is given $\aux$ but only oracle access to $\Qry$, and
it is disallowed from asking any query $q$ for which $q(S_0) \neq
q(S_1)$. \tsnote{I'm not convinced this is the right restriction.
  This says that security is required \emph{only} for properties that are
  true of both sets.  So a scheme with $M=S$ will be trivially secure
  against set membership queries. Do you mean to
  assume that the attacker does not ask~$q$ such that $q(S_0)=q(S_1)$
  because these are pointless?  Otherwise, I don't see a need for restrictions. Maybe we restrict from queries~$q$ that would have the same value for all sets~$S \in \calS$?  (Or all sets of the same size, or...?)}

\tsnote{Is this the right kind of indistinguishability anyway?  It seems to me that we want to say that a representation~$M$ and the public info~$\aux$ tell you nothing (non-trivial) about the set being represented.  To me, this game would be more like, you are handed $(M,\aux)$ and you need to output a query~$q$ such that $q(S_0) \neq q(S_1)$... I don't know, this is tricky.}
%\tsnote{How will the adversary know that a query satisfies
%  this in (say) the case of the classical BF?  We can, of course,
%enforce it in the experiment, but then our resource accounting risks
%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
%\tsnote{Also, we need that, in general, $\aux$ itself
%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
%by the definition in this case.}
\end{enumerate}

>>>>

\item An ``indistinguishability'' definition where either $S_0$ or $S_1$ is used, and the attacker
must determine which. Here the attacker is given $\aux$ but only oracle access to $\Qry$, and
it is disallowed from asking any query $q$ for which $q(S_0) \neq
q(S_1)$. \tsnote{I'm not convinced this is the right restriction.
  This says that security is required \emph{only} for properties that are
  true of both sets.  So a scheme with $M=S$ will be trivially secure
  against set membership queries.  Maybe we restrict from queries~$q$ that are a priori known to have the same value for all sets~$S \in \calS$, or all~$S$ of a given size, etc., as these might be pointless?)}

\tsnote{Is this the right kind of indistinguishability anyway?  It seems to me that we want to say that a representation~$M$ and the public info~$\aux$ tell you nothing (non-trivial) about the set being represented.  One way to capture this would be indistinguishability with respect to the query set~$\calQ$: you are handed $(M,\aux)$ and you need to output a query~$q\in\calQ$ such that $q(S_0) \neq q(S_1)$.  But this doesn't really capture that $(M,\aux)$ on their \emph{own} do not leak information about the set.  (Classical BFs, by the way, essentially leak the number of elements in the set by looking at the Hamming weight of the array.)  I don't know, this is tricky... How do you handle the fact that, under our current syntax, $M$~may contain secrets, e.g. a PRP key?}
%\tsnote{How will the adversary know that a query satisfies
%  this in (say) the case of the classical BF?  We can, of course,
%enforce it in the experiment, but then our resource accounting risks
%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
%\tsnote{Also, we need that, in general, $\aux$ itself
%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
%by the definition in this case.}
\end{enumerate}
